---
title: "Data Exploration Plot"
author: "Olivia Chen"
date: "November 1, 2015"
output: html_document
---


**Take a look of the data**:

- 79.9% are Large Commercial Project
- 20.1% are Small Commercial and All Residential

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
data <- read.csv("f_DFF.csv", header = TRUE)
ggplot(data=data, aes(x=Program)) + geom_histogram(fill="#880011") 
```

**Specific Yield and Program Type**

- Specific Yield = Production (kWh)/Nameplate(Kw)

```{r, echo =FALSE, message=FALSE, warning=FALSE}


ggplot(data,aes(x=Program, y=Specific_Yield)) + geom_boxplot() 
small = subset(data, Program == 'Small Commercial (< 10 kW) and All Residential')
large = subset(data, Program == 'Large Commercial (>= 10 kW)')
summary(small$Specific_Yield)
summary(large$Specific_Yield)
```


**Histogram of Specific Yield**


```{r, echo=FALSE, message=FALSE, warning=FALSE}
    
ggplot(data=data, aes(x=Specific_Yield)) +
  geom_histogram(fill="#880011") +  
  ggtitle("Histogram of Specific Yield") +
  labs(x="Specific Yield", y="Count") 
```

**Specific Yield and Rain fall?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=MTR, y=Specific_Yield)) +
  geom_point(alpha=.2, size=2, color="#880011") +
  ggtitle("Specific Yield vs. Rain") +
  labs(x="Monthly Rain, inches", y="Monthly Specific Yield,\n kwh/kw") 
```

**Specific Yield and Snow fall?**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=TSNW, y=Specific_Yield)) +
  geom_point(alpha=.2, size=2, color="#880011") +
  ggtitle("Specific Yield vs. Snow") +
  labs(x="Monthly Snow, inches", y="Monthly Specific Yield,\n kwh/kw") 
```

**Specific Yield and project coast?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=Total.Cost, y=Specific_Yield)) +
  geom_point(alpha=.2, size=2, color="#880011") +
  ggtitle("Specific Yield vs. Cost") +
  labs(x="Cost", y="Specific Yield,\n kwh/kw") 
```

**Specific Yield and Temperature?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=MNTM, y=Specific_Yield)) +
  geom_point(alpha=.2, size=2, color="#880011") +
  ggtitle("Specific Yield vs. Temperature") +
  labs(x="Monthly Average Temperature (C)", y="Monthly Specific Yield,\n kwh/kw") 
```

**Specific Yield and Tilt?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=CSI.Project.Tilt, y=Specific_Yield)) +
  geom_point(alpha=.2, size=2, color="#880011") +
  ggtitle("Specific Yield vs. Tilt") +
  labs(x="Tilt", y="Monthly Specific Yield,\n kwh/kw") 
```

**Specific Yield and GHI?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=GHI, y=Specific_Yield)) +
  geom_point(alpha=.2, size=2, color="#880011") +
  ggtitle("Specific Yield vs. GHI") +
  labs(x="Monthly GHI", y="Monthly Specific Yield,\n kwh/kw") 
```