---
title: "Data Exploration Plot"
author: "Olivia Chen"
date: "November 1, 2015"
output: html_document
---


**Take a look of the data**:
In 136309 Obervations 

- 79.9% are Large Commercial Project
- 20.1% are Small Commercial and All Residential

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
data <- read.csv("f_DFF.csv", header = TRUE)
ggplot(data=data, aes(x=Program)) + geom_histogram(fill="#880011") 
```

**Specific Yield and Program Type**

- Specific Yield = Production (kWh)/Nameplate(Kw)

```{r, echo =FALSE, message=FALSE, warning=FALSE}
# BASIC THEME
theme.car_chart <- 
  theme(legend.position = "none") +
  theme(plot.title = element_text(size=26, family="Trebuchet MS", face="bold", hjust=0, color="#666666")) +
  theme(axis.title = element_text(size=18, family="Trebuchet MS", face="bold", color="#666666")) +
  theme(axis.title.y = element_text(angle=0)) 


# SCATTERPLOT THEME
theme.car_chart_SCATTER <- theme.car_chart +
  theme(axis.title.x = element_text(hjust=0, vjust=-.5))

# HISTOGRAM THEME
theme.car_chart_HIST <- theme.car_chart +
  theme(axis.title.x = element_text(hjust=0, vjust=-.5))

# SMALL MULTIPLE THEME
theme.car_chart_SMALLM <- theme.car_chart +
  theme(panel.grid.minor = element_blank()) +
  theme(strip.text.x = element_text(size=16, family="Trebuchet MS", face="bold", color="#666666"))

ggplot(data,aes(x=Program, y=Specific_Yield)) + geom_boxplot() 
small = subset(data, Program == 'Small Commercial (< 10 kW) and All Residential')
large = subset(data, Program == 'Large Commercial (>= 10 kW)')
summary(small$Specific_Yield)
summary(large$Specific_Yield)
```

**Specific Yield and Program Administrator?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data, aes(x=Program.Administrator, y=Specific_Yield, fill=Program.Administrator)) +
       geom_boxplot()
```

**Histogram of Specific Yield**


```{r, echo=FALSE, message=FALSE, warning=FALSE}
    
ggplot(data=data, aes(x=Specific_Yield)) +
  geom_histogram(fill="#880011") +  
  ggtitle("Histogram of Specific Yield") +
  labs(x="Specific Yield", y="Count") + 
  theme.car_chart_HIST
```

**Specific Yield and Rain fall?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=MTR, y=Specific_Yield)) +
  geom_point(alpha=.4, size=4, color="#880011") +
  ggtitle("Production Ratio vs. Rain") +
  labs(x="Rain, inches to hundredths", y="Production Ratio,\n kwh/kw") +
  theme.car_chart_SCATTER
```

**Specific Yield and Snow fall?**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=TSNW, y=Specific_Yield)) +
  geom_point(alpha=.4, size=4, color="#880011") +
  ggtitle("Production Ratio vs. Snow") +
  labs(x="Rain, inches to tenths", y="Production Ratio,\n kwh/kw") +
  theme.car_chart_SCATTER
```

**Specific Yield and project coast?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=Total.Cost, y=Specific_Yield)) +
  geom_point(alpha=.4, size=4, color="#880011") +
  ggtitle("Production Ratio vs. Cost") +
  labs(x="Cost", y="Production Ratio,\n kwh/kw") +
  theme.car_chart_SCATTER
```

**Specific Yield and Temperature?**
```{r,echo=FALSE, message=FALSE, warning=FALSE}
ggplot(data=data, aes(x=MNTM, y=Specific_Yield)) +
  geom_point(alpha=.4, size=4, color="#880011") +
  ggtitle("Production Ratio vs. Temperature") +
  labs(x="Monthly Average Temperature (C)", y="Production Ratio,\n kwh/kw") +
  theme.car_chart_SCATTER
```



